Security Properties for Stack Safety

### 2021-05-14 short/main.tex
Tweaked paragraph four

\apt{Here's another stab:}
Our attacker model is very strong, allowing the attacker to execute arbitrary code.
In particular, we do not attempt to prevent \apt{most forms of?} control-flow attacks
\apt{such as ROP?}. The notions of integrity and confidentiality remain useful even
in the absence of normal control flow.
%This formulation not only captures the intuition
%that the callee cannot directly access the caller's state; it also gives a novel
%interpretation of integrity and confidentiality in the presence of control-flow
%attacks.
The key is that every call has a corresponding predicate on states
designated a ``return target''
that defines what it means for that call to truly return: the program counter
must be at the next instruction, and the stack pointer restored to its original
value. A callee may execute the instructions of a return,
but if it does not reach a return target, we simply do not recognize it as a return.
So the callee can be ``active'', and the caller protected, even if the callee is
executing instructions that look like they belong to the caller.

>>>>

\apt{Here's another stab:}
\sna{Tweaked slightly. Trying to make it clear that control flow attacks don't change what we're protecting.}
Our attacker model is very strong, allowing the attacker to execute arbitrary code.
In particular, we do not attempt to prevent control-flow attacks
such as ROP. Even in the absence of normal control flow, confidentiality and integrity
still apply to all of the data they would under more idealized conditions.
%This formulation not only captures the intuition
%that the callee cannot directly access the caller's state; it also gives a novel
%interpretation of integrity and confidentiality in the presence of control-flow
%attacks.
The key is that every call has a corresponding predicate on states
designated a ``return target''
that defines what it means for that call to truly return: the program counter
must be at the next instruction, and the stack pointer restored to its original
value. A callee may execute the instructions of a return,
but if it does not reach a return target, we simply do not recognize it as a return.
So the callee can be ``active'', and the caller protected, even if the callee is
executing instructions that look like they belong to the caller.
